\documentclass[11pt,letterpaper,english]{article}
\usepackage{amsmath}
\usepackage{ae}
\usepackage{colortbl}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
%\usepackage{txfonts} % makes spacing between characters space correctly
%\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

%\usepackage{sectsty}
%\sectionfont{\large}
%\subsectionfont{\normalsize}
%\subsubsectionfont{\normalsize \it}

%\usepackage{caption}
%\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{High-Fidelity Flow Data for Multiscale Bridging} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}



\centering {\bf Curriculum Vitae}\\
{\bf Igor A. Bolotnov}\\
{\bf igor\_bolotnov@ncsu.edu; 518-542-8939} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

Ph.D. in Engineering Physics, Rensselaer Polytechnic Institute, Troy, NY, 2008\\
M.S.  in Engineering Physics, Rensselaer Polytechnic Institute, Troy, NY, 2003\\
B.S. in Applid Mathematics, Bashkir State University, Ufa, Russia, 2002 \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2017--present: Associate Professor, Dept. of Nuclear Engineering, NCSU, Raleigh, NC \\
2011--2017: Assistant Professor, Dept. of Nuclear Engineering, NCSU, Raleigh, NC \\
2008--2010: Post-doctoral Research Associate, Rensselaer Polytechnic Institute, Troy, NY \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Zimmer MD, Bolotnov I. Slug-to-churn vertical two-phase flow regime transition study using an
interface tracking approach. International Journal of Multiphase Flow. 2019; 115:196-206. \\
\item Cambareri JJ, Fang J, Bolotnov I. Simulation Scaling Studies of reactor core two-phase flow
using Direct Numerical Simulation Approach. Nuclear Engineering and Design. 2020;
358:110435. \\
\item M. Li, J. Feng, IA. Bolotnov, Heat Transfer Study in Turbulence Flow with Respect to Low Prandtl Number,  Transactions of 2017 ANS Annual Meeting, San Francisco, CA, June 11–-15, 2017. \\
\item Thomas AM, Fang J, Feng J, Bolotnov I. Estimation of shear-induced lift force in laminar and
turbulent flows. Nuclear Technology. 2015; 190(3):274-291. \\
\item Cambareri JJ, Fang J, Bolotnov I. Simulation Scaling Studies of reactor core two-phase flow
using Direct Numerical Simulation Approach. Nuclear Engineering and Design. 2020;
358:110435. \\
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

Dr. Bolotnov is specialized in computational fluid dynamics applications in nuclear reactor engineering in general, and in multiphase turbulent flow in particular. Dr. Bolotnov research has been supported by the Department of Energy Consortium for Advanced Simulation of LWRs (CASL), the U.S. Nuclear Regulatory Commission, and the National Science Foundation (NSF) among others.

Dr. Bolotnov brings to the project experience and capability with cutting-edge high-performance-computing enabled CFD simulation of complex single- and multi-phase flow. During 2008-2010 as a post-doctoral research associate Dr. Bolotnov actively participated in DOE-funded NERI project that involves modeling and simulation of SFR accident scenarios. His research interest include the large-scale data analysis for complex turbulent flows including statistical and machine-learning based approaches.

}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Humboldt Fellowship for Experienced Researchers (funded by German government), awarded in
Nov. 2018 for research stay in Helmholtz Zentrum Dresden-Rossendorf (Dresden, Germany) for
8 months in 2019/20. \\
\item Scholarly reassignment (sabbatical) in the Fall 2019: supported by Humboldt Fellowship, included seven invited presentations in 5 European countries to establish and enhance collaborations
(including Univ. of Leeds, UK) \\
\item Professional Societies: American Nuclear Society (ANS), member since 2010; Program Chair of
Thermal Hydraulics Division (2019-2022); American Physical Society (APS), Division of Fluid
Dynamics, member since 2010; Sigma Xi, The Scientific Research Honor Society: NCSU
Chapter President for 2016. \\
\item Review Assignments (American Nuclear Society Meetings (2012-present), Physics of Fluids,
Journal of Nuclear Engineering and Design, Journal of Computational Physics, Computers \&
Fluids, International Journal of Multiphase Flow + 22 other journals). \\
\item Program Chair for ANS-THD (2019-2022), Track Chair for NURETH-19 (Brussels, August 2021) and session organizer / chair for multiple ANS Annual and Winter meetings from 2012-2020. Workshop organizer on two-phase flow research
in 2012, 2013, 2017. \\
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt


Abboud, Alexander,	Idaho National Laboratory \\
Baglietto, Emilio,	Massachussets Institute of Technology \\
Bardet, Philip,	George Washington University \\
Dinh, Nam T.,	North Carolina State University \\
Doster, Joseph M.,	North Carolina State University \\
Guillen, Donna P.,	Idaho National Laboratory \\
Gupta, Abhinav,	North Carolina State University \\
Lu, Jiacai,	The John Hopkins University \\
Magolan, Ben,	Massachussets Institute of Technology \\
Youngblood, Robert W.,	Idaho National Laboratory \\
O'Brien, Ellen,	North Carolina State University \\
Peeples, Joanna,	BTI Targetry, LLC \\
Pointer, William D.,	Oak Ridge National Laboratory \\
Rasquin, Michel,	Cenaro \\
Tryggvason, Gretar,	The John Hopkins University \\
Stapellman, Katharina,	North Carolina State University \\
Shaver, Dillon R.,	Argonne National Laboratory \\
Stokely, Matthew H.,	BTI Targetry, LLC \\
Talley, Matthew L.,	North Carolina State University \\
Thomas, Aaron M.,	U.S. Nuclear Regulatory Commission \\
Sun, Xiaodong,	University of Michigan \\
Satpathy, Shrey,	OSISoft LLC

}


\end{flushleft}

\end{document}
