\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{High-Fidelity Flow Data for Multiscale Bridging} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae}\\
{\bf NAM DINH}\\
{\bf e-mail: ntdinh@ncsu.edu, phone: +19195155421} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt
   ~\\
   S.D., 1994, Moscow Power Engineering Institute (Russia), Nuclear Engineering \\
   Ph.D., 1991, Moscow Power Engineering Institute (Russia), Nuclear Engineering \\
   M.S., 1988, Moscow Power Engineering Institute (Russia), Nuclear Engineering \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt
  ~\\
  2013--present, Professor of Nuclear Engineering, North Carolina State University \\
  2009--2012, Laboratory Fellow, Idaho National Laboratory\\
  2008--2009, Directorate Fellow, Idaho National Laboratory\\
  2005--2008, Professor of Nuclear Power Safety, Royal Institute of Technology (Sweden)\\
  1999--2004, Adjunct Associate Professor, University of California, Santa Barbara \\
  1995--1998, Researcher/Group Leader, Royal Institute of Technology (Sweden)
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Hanna B.N., Trieu L.Y.L.Y.T., Son T.C., Dinh N.A.M.T.. An application of ASP in nuclear engineering: Explaining the Three Mile Island nuclear accident scenario. Theory and Practice of Logic Programming. 2020; 20(6):926-941.
\item Bao H, Dinh N, Lin L, Youngblood R, Lane J, Zhang H. Using deep learning to explore local physical similarity for global-scale bridging in thermal-hydraulic simulation. Annals of Nuclear Energy. 2020 November; 147:107684-.
\item Lin L, Athe P, Rouxelin P, Avramova M, Gupta A, Youngblood R, Lane J, Dinh N. Development and assessment of a nearly autonomous management and control system for advanced reactors. Annals of Nuclear Energy. 2021 January; 150:107861-.
\item Chang C, Dinh N. Classification of machine learning frameworks for data-driven thermal fluid models. International Journal of Thermal Sciences. 2019 January; 135:559-579.
\item Liu, Y., Dinh N., Sato Y., and Niceno, B., (2018). Data-Driven Modeling for Boiling Heat Transfer: Using Deep Neural Networks and High-Fidelity Simulation Results. \textit{Applied Thermal Engineering}, 144:305-320.
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt
Reactor safety, Reactor severe accident, Model validation and uncertainty quantification, Multi-phase flow modeling, Physics-informed machine learning
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item General Co-Chair, International Conference "Best Estimate Plus Uncertainty", BEPU-2018, Luca, Italy, May 2018.
\item Executive Committee (2013-2020), Academic Dean (2009-2012), Summer School "Modeling, Experimentation, and Validation".
\item Lecturer, the Frederic Joliot/Otto Hahn (FJOH-2018) Summer School "Maximizing the Benefits of Experiments for the Simulation, Design and Analysis of Reactors" in Aix-en-Provence, France, 2018.
\item Chair (2020-2021), Member (2018-2019). Reactor Safety and Audit Committee, North Carolina State University
\item Plenary Lecturer, NURETH-15 (Italy, 2013), NUTHOS-10 (Japan, 2014), NURETH-16 (Chicago, 2015), ANS-THD Technical Achievement Award lecturer at ANS-2016, NURETH Fellow (2017)
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt

Abhinav Gupta, NCSU \\
Maria Avramova, NCSU\\
Igor Bolotnov, NCSU \\
Xiaodong Sun, U of Michigan \\
Elia, Merzari PSU\\
Carol Smidts, OSU\\
Yohei Sato, PSI (Switzerland)\\
Bojan Niceno, PSI (Switzerland)\\
Robert W. Youngblood, INL \\
Sacit Cetiner, ORNL\\
William D. Pointer,	ORNL \\
Philippe Bardet, GWU\\
Tran Son, NMSU\\
Jeffrey Lane, Zachry Nuclear Engineering\\
}
\end{flushleft}

\end{document}
