

\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Large Eddy Simulation of Rod Bundle Cores} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae }\\
{\bf PAUL FISCHER}\\
{\bf e-mail: fischerp@illinois.edu, phone: +1(217) 300-2031}\\
{\bf e-mail: fischer@mcs.anl.gov, phone: +1(630) 252-6018}\\
 \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

Ph.D., 1989, Mechanical Engineering, Massachusetts Institute of Technology \\
M.S., 1982, Mechanical Engineering, Stanford University \\
B.S., 1981, Mechanical Engineering, Cornell University \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2014--present, Blue Waters Professor, CS \& MechSE, University of Illinois, Urbana-Champaign \\
2014--present, Senior Scientist (part time), Mathematics and Computer Sci. Div., Argonne Nat. Lab.\\
2008-2014, Senior Scientist, Mathematics and Computer Sci. Div., Argonne Nat. Lab. \\
2009-2014, Professor (part-time), Dept. of Statistics, University of Chicago \\
2003-2008, Adjunct Faculty, Dept. of Mech. Eng., University of Illinois, Chicago \\
1999-2014, Senior Fellow, Computation Institute, University of Chicago \\
1998-2008, Mathematician, Mathematics and Computer Sci. Div., Argonne Nat. Lab. \\
1991-1998, Assistant Professor, Div. of Applied Mathematics, Brown U. \\
1990-1991, Postdoctoral Position in Applied Mathematics, Caltech \\
1986-1989, Research Assistant in Mechanical Eng., M.I.T. \\
1983-1986, Sr. Mechanical Engineer, Digital Equipment Corporation \\
1981-1982, Research Assistant in Mechanical Eng., Stanford U./NASA Ames \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
 \item M.O. Deville, P.F. Fischer, and E.H. Mund. High-order methods for incompressible fluid flow.
  Cambridge University Press, Cambridge, 500 p., 2002. \\
 \item K. Mittal, S. Dutta, and P. Fischer, Multirate Timestepping for the Incompressible Navier-Stokes
  Equations in Overlapping Grids arXiv preprint arXiv:2003.00347, 2020. \\
%\item Kento Kaneko, Ping-Hsuan Tsai, and Paul Fischer, Towards Model Order Reduction for
% Fluid-Thermal Analysis, Nucl. Eng. Des. (under review), 2020. \\
 \item Paul Fischer, Misun Min, Thilina Rathnayake, Som Dutta, Tzanio Kolev, Veselin Dobrev, Jean-
  Sylvain Camier, Martin Kronbichler, Tim Warburton, Kasia Swirydowicz, and Jed Brown. Scalability
  of High-Performance PDE Solvers, Int. J. on High Perf. Comput. Appl. (in press), 2020. \\
%\item Ketan Mittal, Som Dutta, and Paul Fischer. Nonconforming Schwarz-spectral element methods
% for incompressible flow. Computers and Fluids, 191, 2019. \\
%\item P. Bello-Maldonado and P.F. Fischer. Scalable low-order finite element preconditioners for highorder
% spectral element Poisson solvers. SIAM J. Sci. Comput.,41 5, S2–S18, 2019.  \\
 \item M. Otten, J. Gong, A. Mametjanov, A. Vose, J. Levesque, P. Fischer, and M. Min. An MPI/OpenACC
  implementation of a high order electromagnetics solver with GPUDirect communication.
  Int. J. High Perf. Comput. Appl., 2016. \\
% \item M. Min and P.F. Fischer, An efficient high-order time integration method for spectral-element
% discontinuous Galerkin simulations in electromagnetics, J. Sci. Comp 57:582–603, 2013. \\
 \item H.M. Tufo and P.F. Fischer. Terascale spectral element algorithms and implementations. In Proc.
of the ACM/IEEE SC99 Conf. on High Performance Networking and Computing, Gordon Bell
Prize. IEEE Computer Soc., CDROM, 1999. \\
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

High-Order Numerical Methods for Partial Differential Equations, Scalable Parallel Algorithms, Iterative Solvers, Parallel Computing, Spectral Element Methods, Computational Fluid Dynamics
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
 \item Gordon Bell Prize for High-Performance Computing, 1999
 \item R\&D 100 Award, 2016
 \item University of Chicago Distinguished Performance Award, 2009
 \item Fellow of American Association for the Advancement of Science (AAAS), 2012
 \item First recipient, Center for Research on Parallel Computation Prize Fellowship, Caltech, 1990
 \item With the help of collaborators and support from DOE’s programs in Applied Math Research and
in Nuclear Energy Advanced Modeling and Simulation, we have developed advanced high-order
algorithms and deployed these in the scalable open-source Navier-Stokes code, Nek5000, which
has over 400 users (https://nek5000.mcs.anl.gov). In addition to providing a scalable high-orderaccuracy
simulation engine, the source distribution provides researchers with direct access to advanced
parallel algorithms and implementations capable of scaling to millions of processors and
billions of gridpoints. \\
\item Reviewer for J.Comp. Phys., SISC, J. Fluid Mech., J. Sci. Comp., SINUM, Nucl. Eng. Des. \\
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt


 S. Balachandar, (U. Florida), \\
 Jed Brown, (UC Boulder), \\
 Veselin Dobrev, (LLNL), \\
 Chistos Frouzakis (ETH Zurich), \\
 Yasin Hassan (TAMU),  \\
 Tzanio Kolev (LLNL),  \\
 Frank Loth (U. Akron), \\
 Elia Merzari (PSU), \\
 Murtazo Nazarov (Uppsala), \\
 Tamay \"Ozg\"okmen (U. Miami),  \\
 Janet Scheel (Occidental), \\
 Philipp Schlatter (KTH), \\
 Michael Sprague (NREL), \\
 Tim Warburton (VT) \\
 }


\end{flushleft}

\end{document}
