\documentclass[11pt,letterpaper,english]{article}
\usepackage{amsmath}
\usepackage{ae}
\usepackage{colortbl}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
%\usepackage{txfonts} % makes spacing between characters space correctly
%\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items 
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

%\usepackage{sectsty}
%\sectionfont{\large}
%\subsectionfont{\normalsize}
%\subsubsectionfont{\normalsize \it}

%\usepackage{caption}
%\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands 

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Proposal Title} \rhead{Graduate Research Assistant} \renewcommand{%
\headrulewidth}{0.0pt}



\centering {\bf Curriculum Vitae ({\emph{2-page limit}})}\\
{\bf Arsen S. Iskhakov}\\
{\bf aiskhak@ncsu.edu; 984-255-3069} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

Ph.D.-student (Nuclear Engineering), North Carolina State University, Raleigh, NC, present \\
Ph.D. (Nuclear Power Plants), Moscow Power Engineering Institute, Moscow, Russia, 2019\\ 
M.Eng. (Nuclear Power Engineering and Thermophysics), Moscow Power Engineering Institute, Moscow, Russia, 2015\\ 
B.Eng. (Technical Physics), Moscow Power Engineering Institute, Moscow, Russia, 2013 \\ 
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2021--present: Graduate Research Assistant, Dept. of Nuclear Engineering, NCSU, Raleigh, NC \\
2019--2020: Junior Researcher, Laboratory of Gas Dynamics and Combustion, Ishlinsky Institute for Problems in Mechanics RAS, Moscow, Russia \\
2016--2019: Teaching Assistant, Dept. of Nuclear Power Plants, Moscow Power Engineering Institute \\
2014--2018: Engineer, Investment Scientific-Production Company “Russian Energy Technologies”, Moscow, Russia \\
2017--2018: Engineer, Laboratory of Thermal Hydraulics, Nuclear Safety Institute of the RAS, Moscow, Russia \\
2014--2016: Engineer, Dept. of Nuclear Power Plants, Moscow Power Engineering Institute \\
2013--2014: Intern Researcher, Joint Institute for High Temperatures of the RAS, Moscow, Russia \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Iskhakov A.S., Melikhov V.I., Melikhov O.I., Yakush S.E., Chung L.T. Hugoniot analysis of experimental data on steam explosion in stratified melt-coolant configuration. Nuclear Engineering and Design. 2019; 347:151-157. \\ 
\item Iskhakov A.S., Melikhov V.I., Melikhov O.I. Hugoniot analysis of energetic molten lead-water interaction. Annals of Nuclear Energy. 2019; 129:437-449.  \\ 
\item Iskhakov A.S., Melikhov V.I., Melikhov O.I., Yakush S.E. Steam generator tube rupture in lead-cooled fast reactors: estimation of impact on neighboring tubes. Nuclear Engineering and Design. 2019; 341:198-208 \\ 
\item Yakush S.E., Iskhakov A.S., Melikhov V.I., Melikhov O.I. Pressure waves due to rapid evaporation of water droplet in liquid lead coolant. Science and Technology of Nuclear Installations. 2018. 2018:3087051.\\ 
\item Iskhakov A.S., Melikhov V.I., Melikhov O.I. Numerical modelling of the hydrodynamic loads applied on the “BREST-300” reactor steam generator tubes during a primary-to-secondary leak accident. MPEI Vestnik. 2017; 3:33-40 [In Russian]  \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

Dr. Iskhakov is specialized in computational fluid dynamics, nuclear thermal hydraulics, and machine learning.
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item  NCSU Provost’s Fellowship (2020-2021), EducationUSA Opportunity Funding (2018-2019), Russian Presidential Scholarship (2014-2015), Moscow Government Scholarship (2014-2015), Rosatom State Atomic Energy Corporation Scholarship (2013-2014), Russian Government Scholarship (2012-2013), MPEI Scholarship for Academic Honors (2009-2015). \\ 
\item Professional Societies: American Nuclear Society (ANS), member since 2020. \\ 
\item Review Assignments (International Journal of Heat and Mass Transfer). \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})} 
{\parindent 16pt

Dinh, Nam T., North Carolina State University \\
Vladimir Melikhov, Moscow Power Engineering Institute  \\
Oleg Melikhov, Moscow Power Engineering Institute \\
Sergey Yakush, Ishlinsky Institute for Problems in Mechanics RAS \\
}


\end{flushleft}

\end{document}
