\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{High-Fidelity Flow Data for Multiscale Bridging} \rhead{E. Merzari et al.} \renewcommand{%
\headrulewidth}{0.0pt}

\centering {\bf Curriculum Vitae}\\
{\bf YANG LIU}\\
{\bf e-mail: yang.liu@anl.gov, phone: +16302520241} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt
   ~\\
   Ph.D., 2018, North Carolina State University, Nuclear Engineering \\
   M.S.,  2013, China Institute of Atomic Energy (China), Nuclear Engineering \\
   B.S.,  2010, Tsinghua University (China), Nuclear Engineering \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt
  ~\\
  2020--present, Nuclear Engineer, Argonne National Laboratory \\
  2019--2020, Post-doctoral Researcher, Argonne National Laboratory\\
  2018--2019, Post-doctoral Researcher, University of Michigan\\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Liu, Y., Hu, R., Balaprakash, P., Brunett, A., Obabko, A. Coarse Mesh CFD Turbulence Prediction for Reactor Transient using Densely Connected Convolutional Networks. In \textit{Transactions of the ANS Winter Meeting}, Virtual, November, 2020.
\item Liu, Y., Sun, X., and Dinh, N.,(2019). Validation and Uncertainty Quantification of Multiphase-CFD Solvers: A Data-Driven Bayesian Framework Supported by High-Resolution Experiments. \textit{Nuclear Engineering and Design}, 354:110200.
\item Liu, Y., Dinh, N., Smith, R.C. and Sun, X., (2019). Uncertainty Quantification of Two-Phase Flow and Boiling Heat Transfer Simulations Through a Data-Driven Modular Bayesian Approach. \textit{International Journal of Heat and Mass Transfer}, 138:1096-1116.
\item \textbf{Liu, Y.} and Dinh N., (2019). Validation and Uncertainty Quantification for Wall Boiling Closure Relations in Multiphase-CFD Solver. \textit{Nuclear Science and Engineering}, 193:81-99.
\item Liu, Y., Dinh N., Sato Y., and Niceno, B., (2018). Data-Driven Modeling for Boiling Heat Transfer: Using Deep Neural Networks and High-Fidelity Simulation Results. \textit{Applied Thermal Engineering}, 144:305-320.
\end{enumerate}

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt
Data-driven modeling, Physics-informed machine learning, Model validation, Uncertainty and sensitivity analysis, Nuclear reactor thermal-hydraulics
}

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Co-PI of Argonne LDRD project "Artificial Intelligence Assisted Safety Modeling and Analysis of Advanced Reactors".
\item Reviewer for Ann. Nucl. Energy, Nucl. Eng. Des., Nucl. Eng. Technol., Nucl. Sci. Eng., Nucl. Technol.,
Prog. Nucl. Energy, Int. J. Heat Mass Transfer, Exp. Therm. Fluid Sci., Math. Probl. Eng., ASME-VVUQ, Heat Transf. Eng.
\item Conference session chair of ATH-2018 NURETH-17, NURETH-18.
\item Member of American Nuclear Society.
\end{enumerate}

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})}
{\parindent 16pt

Rui Hu, ANL \\
Prasanna Balaprakash, ANL\\
Aleksandr Obabko, ANL\\
Nam Dinh, NCSU \\
Xiaodong Sun, U of Michigan \\
Yang Liu, Virginia Tech\\
Ralph C. Smith, NCSU\\
Yohei Sato, PSI (Switzerland)\\
Bojan Niceno, PSI (Switzerland)\\
Acacia Brunett, Oklo Inc.\\
}
\end{flushleft}

\end{document}
